Bot's Guide to Being Human: Investigating the Effect of Conversational Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents

### 2023-02-09 paper.tex
added graphics to paper; added all references from lit review

\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum}

@@

@@

We screened the titles and abstracts of the papers based on the selection criteria below which resulted in 221 papers. Reviewing the full articles of these publication resulted in <X> papers for analysis. A backward/forward search was also performed to find new publications, adding <X> papers to the corpus.

<Add graphic of PRIMSA process>

@@

Categorization of perceptions \newline
Categorization of social cues \newline

\subsection{Dataset Characteristics}
* Year and publication venue
\newline
* Modality - voice vs. text
\newline
* Systems tested - WoZ, prototype, actual applications

@@

\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{heatmap.png}
  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
  \Description{This graph shows the number of papers measuring the effect of conversational architecture elements on different perception measures of conversational agents. Conversational architecture elements are categorized into content (affective language, self-disclosure, humour), format (disfluency, typo, capitalization, speech rate, response delay), and style (lexical alignment, formality, emoticons, prosody). Perceptions are categorized into perception of interaction with an agent (engagement, satisfaction, accuracy), perception of social connection with an agent (intimacy, conversation tone, social presence), and perception of agent's humanness (human-likeness, trustworthiness, personality traits).}
  \label{fig:heatmap}
\end{figure*}

Figure \ref{fig:heatmap}

@@

Content: Humour
* No overall significant difference between conventional method vs. agent using humour for enjoyment. Specifically, men enjoyed the agent's jokes more than women.  \cite{miyamoto2017improving}\cmt{[46]}.

Style: Language Formality
* Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}

@@

@@

@@

[TODO] * Associations between conversational architecture elements and perceptions

@@

@@

\textbf{Format: Prosody}
* There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}

@@

\textbf{Content: Affective language and Style: Disfluency}
* Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}

@@

@@

@@

\textbf{Format: Prosody}
* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{cambre2019one}\cmt{[62]}

@@

@@

\textbf{Format: Prosody}
* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{cambre2019one}\cmt{[62]}

@@

\subsection{Inconsistencies in Perception Measures}

@@

\subsection{Other Influencing Factors}

@@

* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
* Content: Humour - no overall significant difference between conventional method vs. agent using humour for enjoyment. Specifically, men enjoyed the agent's jokes more than women.  \cite{miyamoto2017improving}\cmt{[46]}.
* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability. For easier tasks, system help is not really required. \cite{kraus2020effects}\cmt{[64]}

\subsection{Study Design}

\textbf{Interview vs experiment}
* Humour - what's said vs. study results

\textbf{Observer study vs. interaction study}
* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study. Also, interaction study had lower cognitive demand but no effect in the observer study. \cite{linnemann2018can}\cmt{[15]}
* \cite{zhu2022effects}\cmt{[26]}
* \cite{cox2022does}\cmt{[27]}

\subsection{Modality}

@@

\subsection{Relationship between perceptions}

\subsection{Gaps}

@@

\subsection{Human-human vs. Human-machine}

* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.

\subsection{Ethical Considerations}

@@

Evidence for the influence of voice gender and pitch on stereotypical trait attribution. Active trait attribution is missing as most participants attributes to the negative side of traits for CAs. \cite{cambre2019one}\cmt{[62]}

>>>>

\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}

@@

Design the conversational agents

@@

We screened the titles and abstracts of the papers based on the selection criteria below which resulted in 221 papers. Reviewing the full articles of these publication resulted in 49 papers for analysis. An additional search for related literature was also performed to find new publications, adding 8 more papers to the corpus.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig:prisma.png}
  \caption{Literature search using PRISMA guidelines}
  \label{fig:prisma}
\end{figure}

Figure \ref{fig:prisma}

@@

\subsection{Dataset Characteristics}

* Year and publication venue

\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{fig:paper.png}
  \caption{Stacked barchart of number of papers by year and venue}
  \label{fig:paper}
\end{figure*}

Figure \ref{fig:paper}

\newline
* Modality - voice vs. text Table \ref{tab:modality}

\begin{table}[]
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Modality} & \textbf{No. Papers} \\ \midrule
Voice             & 35                  \\
Text              & 27                  \\ \bottomrule
\end{tabular}%
\caption{Number of paper for voice and text modalities}
\label{tab:modality}
\end{table}

\section{Anthropomorphized Perceptions}

Here is Table \ref{tab:perceptions} for perceptions.

\begin{table*}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllc@{}}
\toprule
 & \textbf{Measure}   & \textbf{Contains}                                  & \textbf{No. Papers} \\ \midrule
\multirow{3}{*}{\textbf{Perception of Interaction with an Agent}}    & Usability       & accuracy, ease of use, efficiency, helpfulness & 23 \\
 & Engagement         & enjoyment, annoyance, desirable, intention to use  & 28         \\
 & Satisfaction       & service satisfaction, quality of interaction       & 12         \\ \midrule
\multirow{3}{*}{\textbf{Perception of Agent's Ability}}              & Intelligence    & knowledgeable, intelligent, expertise                             & 11 \\
 & Competence         & competent, capable                                 & 4          \\
 & Trust              & credibility, trustworthy, truthfulness, confidence & 15         \\ \midrule
\multirow{3}{*}{\textbf{Perception of Social Connection with Agent}} & Social Presence & connectedness, familiarity, similarity, psychological distance    & 18 \\
 & Conversation Tone  & appropriate, expressive, empathetic, persuasive    & 13         \\
 & Intimacy           & intimate, rapport, quality of relationship         & 7          \\ \midrule
\multirow{2}{*}{\textbf{Perception of Agent's Humanness}}            & Human-likeness  & human-like, natural, artificial, machine-like                     & 20 \\
 & Personality Traits & friendly, kind, warm, creepy, likeable, polite     & 27         \\ \bottomrule
\end{tabular}%
}
\caption{Perception measures}
\label{tab:perceptions}
\end{table*}

%\multirow{3}{*}{\parbox{2cm}{\textbf{Perception of Interaction with an Agent}}} & Usability & accuracy, ease of use, efficiency, helpfulness &

%Usability
%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{kim2020can}\cmt{[24]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{healey2013relating}\cmt{[39]}\cite{miehle2018exploring}\cmt{[51]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{kraus2020effects}\cmt{[64]}\cite{cuadra2021my}\cmt{[67]}\cite{roy2021users}\cmt{[71]}\cite{chan2021kinvoices}\cmt{[74]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}\cite{haas2022keep}\cmt{[78]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{kim2019comparing}\cmt{[89]}

%Engagement
%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{lee2020hear}\cmt{[23]}\cite{kim2020can}\cmt{[24]}\cite{zhu2022effects}\cmt{[26]}\cite{cox2022does}\cmt{[27]}\cite{ma2022ask}\cmt{[29]}\cite{andrews2012system}\cmt{[38]}\cite{healey2013relating}\cmt{[39]}\cite{miyamoto2017improving}\cmt{[46]}\cite{miehle2018exploring}\cmt{[51]}\cite{fadhil2018effect}\cmt{[52]}\cite{ceha2021can}\cmt{[57]}\cite{elsholz2019exploring}\cmt{[61]}\cite{cuadra2021my}\cmt{[67]}\cite{volkel2021examining}\cmt{[69]}\cite{roy2021users}\cmt{[71]}\cite{yang2021effect}\cmt{[72]}\cite{xiao2021let}\cmt{[73]}\cite{chan2021kinvoices}\cmt{[74]}\cite{volkel2022user}\cmt{[75]}\cite{ceha2022expressive}\cmt{[77]}\cite{go2021conversational}\cmt{[80]}\cite{jestin2022effects}\cmt{[81]}\cite{moilanen2022measuring}\cmt{[82]}\cite{kim2019comparing}\cmt{[89]}

%Satisfaction                                                                 
%\cite{pfeifer2009should}\cmt{[12]}\cite{gnewuch2018faster}\cmt{[19]}\cite{diederich2019emulating}\cmt{[25]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{hoegen2019end}\cmt{[31]}\cite{yang2017perceived}\cmt{[44]}\cite{choi2020nobody}\cmt{[54]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{roy2021users}\cmt{[71]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}

Categorization of social cues \newline
* adapted from Taxonomy of social cues
* added a middle layer
* combined elements as we are studying disembodied agents

\section{Conversation Architecture}

Here is Table \ref{tab:cues} for conversation architecture elements.

\begin{table*}[]
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllc@{}}
\toprule
 & \textbf{Measure}      & \textbf{Contains}                                      & \multicolumn{1}{l}{\textbf{No. Papers}} \\ \midrule
\multirow{4}{*}{\textbf{Linguistic Content}}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
 & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
 & Humour                & humorous content, jokes                                & 5                                       \\
 & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
\multirow{4}{*}{\textbf{Linguistic Style}}      & Formality          & formal vs. casual, honorific expressions                               & 9  \\
 & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
 & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
 & Disfluency            & fillers, interjections, repetitions                    & 5                                       \\ \midrule
\multirow{3}{*}{\textbf{Non-Linguistic Format}} & Prosody            & pitch, intonation, speech rate, spoken accent                          & 12 \\
 & Text Variation        & typo, capitalization, response delay, typing indicator & 5                                       \\
 & Emotional Cue         & emoticons, laughter                                    & 6                                       \\ \bottomrule
\end{tabular}%
%}
\caption{Conversation architecture elements}
\label{tab:cues}
\end{table*}

@@

\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{fig:heatmap-impact.png}
  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
  \Description{This graph shows the number of papers measuring the effect of conversational architecture elements on different perception measures of conversational agents. Conversational architecture elements are categorized into content (affective language, self-disclosure, humour), format (disfluency, typo, capitalization, speech rate, response delay), and style (lexical alignment, formality, emoticons, prosody). Perceptions are categorized into perception of interaction with an agent (engagement, satisfaction, accuracy), perception of social connection with an agent (intimacy, conversation tone, social presence), and perception of agent's humanness (human-likeness, trustworthiness, personality traits).}
  \label{fig:heatmap-impact}
\end{figure*}

Figure \ref{fig:heatmap-impact}

@@

\textbf{Content: Humour}
* No overall significant difference between conventional method vs. agent using humour for enjoyment. Specifically, men enjoyed the agent's jokes more than women.  \cite{miyamoto2017improving}\cmt{[46]}.
* Motivation to continue the conversation significant increased after day 2 for the humorous agent \cite{go2021conversational}\cmt{[80]}

\textbf{Style: Language Formality}
* Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}
* commanding/formal wording was rated significantly more useful than the informal wording; while the informal wording was rated as significantly more annoying than the commanding/formal wording. No impact on desirability. \cite{jestin2022effects}\cmt{[81]}
* High conscientiousness (formal) and high extroversion (casual) chatbot personality have higher user engagement. \cite{moilanen2022measuring}\cmt{[82]}
* Analysis of ease of use reveals that there are no significant main effects for platform questionnaire vs. chatbot, and conversational style formal vs. casual.\cite{kim2019comparing}\cmt{[89]}

\textbf{Social talk / elaborate}
* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
* usefulness depended on the task \cite{haas2022keep}\cmt{[78]}
* High extroversion chatbot personality have the higher user engagement \cite{moilanen2022measuring}\cmt{[82]}

\textbf{Disfluency}
* Using moderately repetitive utterances resulted in higher desire to continue the dialogue with the agent. \cite{yang2021effect}\cmt{[72]}
* Interjections did not have any impacts of cognitive workload \cite{ceha2022expressive}\cmt{[77]}

\textbf{Proactive}
* Different framing has impacts on the perceived disruptiveness of the agent. \cite{xiao2021let}\cmt{[73]}

\textbf{Prosody}
* No impact on annoying, undesirable, useful \cite{jestin2022effects}\cmt{[81]}
* Dialog-style conversation using prosodic cues is rated as less easy to understand than the reading-style \cite{misu2011toward}\cmt{[83]}

\textbf{Combined}
* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) all personalities have similar usability ratings. Also, users have greater desire to interact with the extraverted chatbot \cite{volkel2022user}\cmt{[75]}
* (Politeness: affective language + elaborateness of speech) no impact on usability \cite{hu2022polite}\cmt{[76]}

@@

\textbf{Social talk}
* Introverted agent is more efficient. \cite{roy2021users}\cmt{[71]}
* Efficiency depended on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* commanding/formal wording was rated significantly more effective than informal wording \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* No impact on effectiveness \cite{jestin2022effects}\cmt{[81]}

\textbf{Repair}
* One reason for choosing repair strategy preference is efficiency and efficacy. \cite{ashktorab2019resilient}\cmt{[88]}

@@

\textbf{Social talk}
* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}

\textbf{Combined}
* (Politeness: affective language + elaborateness of speech) no impact on user satisfaction \cite{hu2022polite}\cmt{[76]}

@@

\textit{To be incorporated}

\textbf{Repair}
* perceived quality of the interaction is muhc higher in repair condition when the agent made a mistake; rating is lower if no mistake was present. \cite{cuadra2021my}\cmt{[67]}

@@

\textbf{Prosody}
* VA using kin's voice is rated as more intelligent. \cite{chan2021kinvoices}\cmt{[74]}

\textbf{Repair}
* One reason for choosing repair strategy preference is perceived intelligence and capability. \cite{ashktorab2019resilient}\cmt{[88]}

@@

\textbf{Format: Prosody}
* There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}

@@

\textbf{Content: Affective language and Style: Disfluency}
* Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}
* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

\textbf{Prosody}
* VA using kin's voice is rated as more socially present and closer psychological connection with user. \cite{chan2021kinvoices}\cmt{[74]}
* voice plus social condition has higher social presence than the social condition \cite{lubold2016effects}\cmt{[86]}

\textbf{Humour}
* Familiarity with the agent is rated higher at the end of the study (day 7) compared to non-humorous agent \cite{go2021conversational}\cmt{[80]}

\textbf{Laughter}
* Laughter had no impact on social presence of an agent \cite{niewiadomski2013laugh}\cmt{[85]}

@@

\textbf{Disfluency}
* Using moderately repetitive utterances resulted in higher perceived empathy. \cite{yang2021effect}\cmt{[72]}

\textbf{Language Formality}
* commanding/formal wording was rated significantly more appropriate and assertive than informal wording \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* No impact on appropriate and assertive \cite{jestin2022effects}\cmt{[81]}
* Dialog-style conversation using prosodic cues is rated as more appropriate than the reading-style \cite{misu2011toward}\cmt{[83]}

@@

\textbf{Disfluency}
* Interjections did not have any impacts of quality of relationship, but it did result in higher emotional rapport. \cite{ceha2022expressive}\cmt{[77]}

\textbf{Affective Language}
* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

\textbf{Prosody}
* voice and social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

@@

\textbf{Prosody}
* VA using kin's voice is rated as more human-like. \cite{chan2021kinvoices}\cmt{[74]}
* Dialog-style conversation using prosodic cues is rated as less human-like than the reading-style \cite{misu2011toward}\cmt{[83]}

\textbf{Social talk / Elaborateness}
* Naturalness depends on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* No impact on artificial or humanlike perceptions \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* Matthew voice is rated as least artificial  \cite{jestin2022effects}\cmt{[81]}

\textbf{Laughter}
* Laughter was not rated as natural in an agent \cite{niewiadomski2013laugh}\cmt{[85]}

\textbf{Combined}
* (Politeness: affective language + elaborateness of speech) no impact on likability, but positive politeness interactions are rated as more polite \cite{hu2022polite}\cmt{[76]}

\textbf{Repair}
* One reason for choosing repair strategy preference is naturalness. \cite{ashktorab2019resilient}\cmt{[88]}

@@

\textit{To be incorporated}

@@

\textbf{Format: Prosody}
* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{tolmeijer2021female}\cmt{[62]}
* VA using kin's voice is rated as more likable. \cite{chan2021kinvoices}\cmt{[74]}
* No impact on entertaining or friendly  \cite{jestin2022effects}\cmt{[81]}

\textbf{Repair}
* When VA corrected in the condition it didn't make a mistake, it is seen as anxious. Otherwise it is perceived as calm and emotionally stable. \cite{cuadra2021my}\cmt{[67]}
* One reason for choosing repair strategy preference is politeness. \cite{ashktorab2019resilient}\cmt{[88]}

\textbf{Social talk}
* Using more social talk is positive correlated with extroversion. \cite{volkel2021manipulating}\cmt{[68]}
* Not significant importance between introvert and extrovert agents. \cite{roy2021users}\cmt{[71]}
* Likability depends on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* Informal wording was rated as strongly more entertaining and friendly than the commanding/formal wording. \cite{jestin2022effects}\cmt{[81]}

\textbf{Agreeableness}
* Being highly confrontational (less agreeable) is rated as less conscientious \cite{volkel2021manipulating}\cmt{[68]}
* Designing for more agreeable resulted in personality rated as more agreeable \cite{volkel2021examining}\cmt{[69]}

\textbf{Combined}
* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) extraverted personality rated as more extraverted \cite{volkel2022user}\cmt{[75]}

\textbf{Format: Prosody}
* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{tolmeijer2021female}\cmt{[62]}
* No impact on trustworthiness  \cite{jestin2022effects}\cmt{[81]}

\textbf{Language Formality}
* No impact on trustworthiness \cite{jestin2022effects}\cmt{[81]}

@@

\subsection{RQ1 - synthesis of conversation architecture elements}

Sometimes a study is covering multiple conversational element cues, hard to break it out. For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure. Need to break it down.

Also, breaking down "personalities" to its core components.

\subsection{RQ2 - synthesis of perceptions}

\subsubsection{Inconsistencies in Perception Measures}

@@

\subsubsection{Relationship between perceptions}

VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}

\subsection{RQ3 - relationship between conversation architecture elements and perceptions}

\subsubsection{Other Influencing Factors}

@@

* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
* Content: Humour - no overall significant difference between conventional method vs. agent using humour for enjoyment. Specifically, men enjoyed the agent's jokes more than women.  \cite{miyamoto2017improving}\cmt{[46]}.
* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability. For easier tasks, system help is not really required. \cite{kraus2020effects}\cmt{[64]}
* Preference for the level of social talk depended on the task, even within the same transactional context, as users preferred high level for playing a song, but low level for writing a text. \cite{volkel2021manipulating}\cmt{[68]}
* Correlation between user's personality of agreeableness vs. preference for agreeable level of chatbot \cite{volkel2021examining}\cmt{[69]}
* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
* Participants felt irritated when humorous statements were made when they talked about experiencing sadness \cite{go2021conversational}\cmt{[80]}

%\subsubsection{Study Design}

%\textbf{Interview vs experiment}
%* Humour - what's said vs. study results

%\textbf{Observer study vs. interaction study}
%* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study. Also, interaction study had lower cognitive demand but no effect in the observer study. \cite{linnemann2018can}\cmt{[15]}
%* \cite{zhu2022effects}\cmt{[26]}
%* \cite{cox2022does}\cmt{[27]}

\subsubsection{Modality}

@@

\subsubsection{Gaps}

@@

%\subsubsection{Human-human vs. Human-machine}

%* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.

\subsubsection{Ethical Considerations}

@@

Evidence for the influence of voice gender and pitch on stereotypical trait attribution. Active trait attribution is missing as most participants attributes to the negative side of traits for CAs. \cite{tolmeijer2021female}\cmt{[62]}

The social and emotional benefits of self-repair in interaction need to be balanced against the creepiness of the monitoring and modelling needed to make self-repair possible. \cite{cuadra2021my}\cmt{[67]}
